---
title: "R Markdown w/ a Shiny runtime"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
```

Install the `shiny` package before attempting to render this document.

# Creating a simple UI

See help page for [`shiny::selectInput()`](https://www.rdocumentation.org/packages/shiny.semantic/versions/0.4.3/topics/selectInput). The most usful input options at this stage are:

- checkboxGroupInput()
- checkboxInput()
- numericInput()
- radioButtons()
- sliderInput()

Other input options, useful in other situations, include:

- actionButton()
- dateInput()
- dateRangeInput()
- fileInput()
- passwordInput()
- submitButton()
- textAreaInput()
- textInput()
- varSelectInput()

## Use

To use the input UI, make an `inputPanel({})`, and use the values in a `render*({})` function. Here, `renderPlot({})`, but there are other oututs you can use.

```

inputPanel({
  # input function here...
})

renderPlot({
  # output plot here ...
})

```

The first argument of an input UI is the name of that input in the list called `input`, e.g. `shape`. Access it by name in the `render*()` function, e.g. `input$shape`.

```{r echo = FALSE}

inputPanel({
  radioButtons("shape", label = "Circle:",
               c(16, 1))
})

renderPlot({
  ggplot(mtcars, aes(mpg, wt)) +
    geom_point(shape = as.numeric(input$shape), 
               alpha = 0.75, size = 10)
})

```

Above, we convert the `chr` to a `numeric` value for input in the plot. 